Fusion Moves for Correlation Clustering

### 2014-11-11 paper/introduction-new.tex

Another line of work maintains valid partitionings throughout, either by using a cluster representation in terms of labels \cite{bagon_2011_arxiv} or in terms of cut edges \cite{beier_2014_cvpr}. 
The former suffers \cite{beier} from the degeneracy of a label presentation \cite{kappes}, while the latter is highly efficient only for planar graphs.
% Working on contracted nodes has previously been explored in \cite{kroeger_2013_miccai}. 
An other branch of research uses move making algorithm 
to optimize correlation clustering~\cite{bansal_2004_ml,beier_2014_cvpr,Kernighan-1970}.
Starting with an initial segmentation, auxiliary problems are solved that 
strictly improve the segmentation.

Bansal and Bagon propose a modified $\alpha-$expansion~\cite{bansal_2004_ml} 
algorithm suitable for correlation clustering, that allows all variables to 
change to cluster $\alpha$ in a single move. While the authors claim that this
scales to large scale data, in~\cite{beier_2014_cvpr} it has been shown that 
this is not the case in general. This is not surprising because the auxiliary 
problems can have as many variables as the original problem.

A more efficient move making method has been presented by Beier \etal~\cite{beier_2014_cvpr}.
Their Cut, Glue and Cut method iteratively re-optimizes the cuts between adjacent clusters of the current solution.
While this method scales better then  modified $\alpha-$expansion, it still faces three problems:
Firstly, the subproblems can be as large as the original problem,
secondly, the subproblems are max-cut problems on non-planar graphs that are NP-hard 
and even the used approximation has high polynomial complexity.
This limits the method, to be applicable to huge problems. The same holds for the 
method of Kernighan and Lin~\cite{Kernighan-1970}.

   % \begin{itemize}
   % \item Multicut~\cite{kappes_2011_emmcvpr}
   % \item Expand and Explorer~\cite{bagon_2011_arxiv}
   % \item Fast Planar CC~\cite{yarkony_2012_eccv}
   % \item Break and Conquer \cite{alush_2013_simbad}.
   % \item Cut Glue And Cut~\cite{beier_2014_cvpr}
   % \end{itemize}

For energy minimization problems fusion moves have become increasingly popular~\cite{Lempitsky-2010,kappes_2014_ws}.
For many large scale computer vision applications fusion moves lead to good approximations
with state of the art any time performance~\cite{kappes_2014_ws}.

Finally, there are heuristic methods such as ...

\vspace{0.1cm}
\noindent \textbf{Outline:} {\bf If we are short of space, the following can be ommited:}
In sec.~\ref{sec:problem_formulation} we will give a 
detailed problem definition where we introduce 
the correlation clustering objective.
In sec.~\ref{sec:related_work} we will 
discuss existing methods for correlation 
clustering and briefly explain the concept of fusion moves.
In sec: ~\ref{sec:cc_fm} we describe our proposed
method and show the properties of the algorithm.
In sec.~\ref{sec:exp} we show an evaluation
of the method on existing parameter  and discuss the effects of parameters.
Future work will be discussed in sec. \ref{sec:future} and
we will conclude in ~\ref{sec:conclusion}.
%-------------------------------------------------------------------------

@@

\section{Related Work}\label{sec:related_work}%
%
Due to the ambiguity of formulation~\ref{eq:nodeproblem},
a major branch of research has focused on solving 
relaxations of eq.~\ref{eq:edgeproblem}.
To keep the objective and system of inequalities small, they 
work on sparse graphs and
use cutting plane methods
in combination with (integer) linear programming and efficient 
separation procedures~\cite{kappes_2011_emmcvpr,andres_2011_iccv,kappes_2013_arxiv}.

With no time restrictions and integer constraints these methods can solve the problem to global optimality.
For huge problems both, separation and solving the ILP in each round, becomes very time consuming.

For planar problems, Yarkony \etal~\cite{yarkony_2012_eccv} 
suggested a column generating strategy for the outer LP-relaxation
that includes all cycle-inequalities of problem \ref{eq:edgeproblem}.
The column generation base on solving planar max cut instances.
While this method is fast, 
it only solve a relaxation of the problem and so requires additional rounding strategies,
lacks of a practical stopping condition for the column generation,
and most important  is restricted to planar problems.

An other branch of research uses move making algorithm 
to optimize correlation clustering~\cite{bansal_2004_ml,beier_2014_cvpr,Kernighan-1970}.
Starting with an initial segmentation, auxiliary problems are solved that 
strictly improve the segmentation.

Bansal and Bagon propose a modified $\alpha-$expansion~\cite{bansal_2004_ml} 
algorithm suitable for correlation clustering, that allows all variables to 
change to cluster $\alpha$ in a single move. While the authors claim that this
scales to large scale data, in~\cite{beier_2014_cvpr} it has been shown that 
this is not the case in general. This is not surprising because the auxiliary 
problems can have as many variables as the original problem.

A more efficient move making method has been presented by Beier \etal~\cite{beier_2014_cvpr}.
Their Cut, Glue and Cut method iteratively re-optimizes the cuts between adjacent clusters of the current solution.
While this method scales better then  modified $\alpha-$expansion, it still faces three problems:
Firstly, the subproblems can be as large as the original problem,
secondly, the subproblems are max-cut problems on non-planar graphs that are NP-hard 
and even the used approximation has high polynomial complexity.
This limits the method, to be applicable to huge problems. The same holds for the 
method of Kernighan and Lin~\cite{Kernighan-1970}.

   % \begin{itemize}
   % \item Multicut~\cite{kappes_2011_emmcvpr}
   % \item Expand and Explorer~\cite{bagon_2011_arxiv}
   % \item Fast Planar CC~\cite{yarkony_2012_eccv}
   % \item Break and Conquer \cite{alush_2013_simbad}.
   % \item Cut Glue And Cut~\cite{beier_2014_cvpr}
   % \end{itemize}

For energy minimization problems fusion moves have become increasingly popular~\cite{Lempitsky-2010,kappes_2014_ws}.
For many large scale computer vision applications fusion moves lead to good approximations
with state of the art any time performance~\cite{kappes_2014_ws}.

The fusion move algorithm iteratively fuse the current best solution with a proposal solutions
by optimizing over the subspace spanned by the two labeling. 
Due to the ambiguity of a node-labeling, fusion moves can not be applied directly for correlation clustering.
We will show how to overcome this point later.

\input{inputs/fig_hc_alg.tex}

Outside computer vision greedy methods has been suggested for correlation clustering problems, see \cite{Elsner-2009} for an overview.
A common greedy approach~\cite{Soon-2001,Ng-2002,Elsner-2008} is to randomly permute the nodes and than assign 
iteratively each node to an existing cluster or create a new cluster if costs cannot be decreased by assigning to a cluster.
%Common assigning strategies are:
%\emph{BEST}; assign to cluster which is linked by the most positive edge~\cite{Ng-2002},
%\emph{FIRST}; Assign to the cluster which is first linked by a positive edge~\cite{Soon-2001}, and
%\emph{VOTE}; Assign to cluster that minimizes objective function~\cite{Elsner-2008}.
%
The PIVOT Algorithm~\cite{Ailon-2008} iterate over all nodes in random order.
If the node is not assigned it construct a cluster containing the node and all its 
unassigned positively linked neighbors.  
%
%Typically these algorithms started for many random permutations, 
%and pick the clustering with best objective value.

A widely use post-processing method is  Best One Element Move (BOEM)~\cite{Gionis-2007}.
Start with an initial clustering one node is removed from a cluster and reassigned to an existing or new cluster such that the costs are minimized.
BEOM stops if no move can decrease the costs.

% \subsection{Karger-Stein Algorithms}
% Use randomized procedure to reduce the number of nodes / edges to a reasonable 
% number.
% On the smaller graph, more expensive solvers are used.

%\input{inputs/fig_hc_alg.tex}

>>>>

Another line of work uses move making algorithm 
to optimize correlation clustering~\cite{bansal_2004_ml,beier_2014_cvpr,Kernighan-1970}.
Starting with an initial segmentation, auxiliary max-cut problems are approximately solved,
such that the segmentation is strictly improved.
As shown by Beier \etal~\cite{beier_2014_cvpr} only CGC~\cite{beier_2014_cvpr} 
can deal with large scale problems, but can also suffer on very large auxiliary problems.

Outside computer vision greedy methods~\cite{Soon-2001,Ng-2002,Gionis-2007,Elsner-2008,Ailon-2008} has been suggested for correlation clustering problems, see \cite{Elsner-2009} for an overview.
The PIVOT Algorithm~\cite{Ailon-2008} iterate over all nodes in random order.
If the node is not assigned it construct a cluster containing the node and all its 
unassigned positively linked neighbors.  
%
A widely use post-processing method is  Best One Element Move (BOEM)~\cite{Gionis-2007}, which iteratively reassigned nodes to clusters.

For energy minimization problems fusion moves have become increasingly popular~\cite{Lempitsky-2010,kappes_2014_ws}.
For many large scale computer vision applications fusion moves lead to good approximations
with state of the art any time performance~\cite{kappes_2014_ws}.
Due to the ambiguity of a node-labeling, classical fusion moves~\cite{Lempitsky-2010} can not be applied directly for correlation clustering.
We will show how to overcome this point later.

\vspace{0.1cm}
\noindent \textbf{Outline:} 
In sec.~\ref{sec:problem_formulation} we will give a 
detailed problem definition where we introduce 
the correlation clustering objective.
In sec.~\ref{sec:related_work} we will 
discuss existing methods for correlation 
clustering and briefly explain the concept of fusion moves.
In sec: ~\ref{sec:cc_fm} we describe our proposed
method and show the properties of the algorithm.
In sec.~\ref{sec:exp} we show an evaluation
of the method on existing parameter  and discuss the effects of parameters.
Future work will be discussed in sec. \ref{sec:future} and
we will conclude in ~\ref{sec:conclusion}.
%-------------------------------------------------------------------------

@@
